---
title: "YuDesk2"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, echo=FALSE}
library(tidyverse)
## library(lubridate)
## library(scales)
library(flexdashboard)
library(yulr)

## TODO: Fix the hardcoding of the data directory.

## yudesk_data_dir <- paste0(Sys.getenv("DASHYUL_DATA"), "/viz/yudesk/")
yudesk_data_dir <- "/dashyul/data/viz/yudesk/"

yudesk_data_file <- paste0(yudesk_data_dir, "yudesk-summary.rds")

l <- readRDS(yudesk_data_file)

l$month_name <- factor(l$month_name, levels = c("Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug"))

l$location.name <- as.factor(l$location.name)

l$library.name <- as.factor(l$library.name)
libraries <- levels(l$library.name)

l$ayear <- as.factor(l$ayear)

question.types <- c("1. Non-Resource", "2. Skill-Based: Tech Support", "3. Skill-Based: Non-Technical", "4. Strategy-Based", "5. Specialized")
research.questions <- question.types[4:5]

current_academic_year <- academic_year(Sys.Date())

```

Sidebar {.sidebar}
=====================================
(Data goes to end of last month.)

```{r}
## selectInput("library_name", "Library", libraries, selected = "Scott")

## library <- reactive({
##     l %>% filter(library.name == input$library_name)
## })

## locations_vector <- reactive({
##     as.vector((library() %>% distinct(location.name))$location.name)
## })

## output$location_choice_menu <- renderUI({
##     selectInput("location_name", "Location", locations_vector())
## })
## uiOutput("location_choice_menu")


## formats_vector <- reactive({
##     as.vector((library() %>% distinct(question.format))$question.format)
## })

## output$format_choice_menu <- renderUI({
##     ## selectInput("question_format", "Format", formats_vector(), selected = formats_vector(), multiple = TRUE)
##     checkboxGroupInput("question_format", "Format", formats_vector(), selected = formats_vector())
## })
## uiOutput("format_choice_menu")

## , question.format %in% input$question_format

checkboxGroupInput("ayear", "Academic year", seq(2010, current_academic_year, by = 1), selected = seq(2011, current_academic_year, by = 1))

checkboxGroupInput("question_type", label = "Question type", choices = c("1" = "1. Non-Resource", "2" = "2. Skill-Based: Tech Support", "3" = "3. Skill-Based: Non-Technical", "4" = "4. Strategy-Based", "5" = "5. Specialized"), selected = c("1. Non-Resource", "2. Skill-Based: Tech Support", "3. Skill-Based: Non-Technical", "4. Strategy-Based", "5. Specialized"))

subsetted_by_sidebar <- reactive({
    l %>% filter(ayear %in% input$ayear, question.type %in% input$question_type)
})

all_questions <- reactive({
    l %>% filter(ayear %in% input$ayear, question.type %in% input$question_type) %>% group_by(ayear, month_name) %>% summarise(total = sum(count))
})

subset_by_library_and_location <- function (library_name = NULL, location_name = NULL) {
    subset <- subsetted_by_sidebar()
    if (! is.null(library_name)) {
        subset <- subset %>% filter(library.name == library_name)
    }
    if (! is.null(location_name)) {
        subset <- subset %>% filter(location.name == location_name)
    }
   return(subset)
}

construct_annual_chart <- function(library_name = NULL, location_name = NULL) {
    annual_data <- subset_by_library_and_location(library_name, location_name)
    annual_data <- annual_data %>% count(ayear, name = "total", wt = n)
    if (! is.null(library_name)) {
        chart_title <- library_name
    } else {
        chart_title <- "YUL"
    }
    if (! is.null(location_name)) {
        chart_title <- paste(chart_title, " / ", location_name)
    }
    chart_title <- paste(chart_title, " / annual")
    ggplot(annual_data, aes(x = ayear, y = total)) +
      geom_col() +
      labs(title = chart_title, x = "Academic year", y = "") +
      theme(axis.text = element_text(size = 10), axis.text.x = element_text(angle = 90))
}

construct_monthly_chart <- function(library_name = NULL, location_name = NULL) {
    monthly_data <- subset_by_library_and_location(library_name, location_name)
    monthly_data <- monthly_data %>% count(ayear, month_name, name = "total", wt = n)
    if (! is.null(library_name)) {
        chart_title <- library_name
    } else {
        chart_title <- "YUL"
    }
    if (! is.null(location_name)) {
        chart_title <- paste(chart_title, " / ", location_name)
    }
    chart_title <- paste(chart_title, " / monthly")
    ggplot(monthly_data, aes(x = ayear, y = total)) +
      geom_col() +
      facet_grid(. ~ month_name) +
      labs(title = chart_title, x = "Academic year", y = "") +
      theme(axis.text = element_text(size = 10), axis.text.x = element_text(angle = 90))
}

```

YUL
=====================================

Column
-------------------------------------

### Annual

```{r}
renderPlot({
    construct_annual_chart()
})
```

### Monthly

```{r}
renderPlot({
    construct_monthly_chart()
})
```

ASC
=====================================


Row {.tabset}
-------------------------------------

### All (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "ASC")
})
 ```

### All (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "ASC")
})
 ```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "ASC", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "ASC", location_name = "Office")
})
```

### Reference Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "ASC", location_name = "Reference Desk")
})
```

### Reference Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "ASC", location_name = "Reference Desk")
})
```

Ask a Librarian
=====================================


Row {.tabset}
-------------------------------------

### All (annual)


```{r}
renderPlot({
    construct_annual_chart(library_name = "Ask a Librarian")
})
```

### All (monthly)


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Ask a Librarian")
})
 ```


AskUs
=====================================


Row {.tabset}
-------------------------------------

### All


```{r}
renderPlot({
    construct_monthly_chart(library_name = "AskUs")
})
```

### Circulation Desk

```{r}
renderPlot({
    construct_monthly_chart(library_name = "AskUs", location_name = "Circulation Desk")
})
```


Bronfman
=====================================


Row {.tabset}
-------------------------------------

### All (annual)


```{r}
renderPlot({
    construct_annual_chart(library_name = "Bronfman")
})
```

### All (monthly)


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Bronfman")
})
 ```

### Circulation Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Bronfman", location_name = "Circulation Desk")
})
```

### Circulation Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Bronfman", location_name = "Circulation Desk")
})
```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Bronfman", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Bronfman", location_name = "Office")
})
```

### Reference Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Bronfman", location_name = "Reference Desk")
})
```

### Reference Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Bronfman", location_name = "Reference Desk")
})
```


Frost
=====================================


Row {.tabset}
-------------------------------------

### All (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Frost")
})
 ```

### All (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Frost")
})
 ```

### Circulation Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Frost", location_name = "Circulation Desk")
})
```

### Circulation Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Frost", location_name = "Circulation Desk")
})
```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Frost", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Frost", location_name = "Office")
})
```

### Reference Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Frost", location_name = "Reference Desk")
})
```

### Reference Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Frost", location_name = "Reference Desk")
})
```

Maps
=====================================


Row {.tabset}
-------------------------------------

### All (annual)


```{r}
renderPlot({
    construct_annual_chart(library_name = "Maps")
})
 ```

### All (monthly)


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Maps")
})
 ```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Maps", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Maps", location_name = "Office")
})
```

### Reference Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Maps", location_name = "Reference Desk")
})
```

### Reference Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Maps", location_name = "Reference Desk")
})
```


Osgoode
=====================================


Row {.tabset}
-------------------------------------

### All


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Osgoode")
})
 ```

### Office

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Osgoode", location_name = "Office")
})
```

### Reference Desk

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Osgoode", location_name = "Reference Desk")
})
```


Scott
=====================================


Row {.tabset}
-------------------------------------

### All


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Scott")
})
```

### Consultation Desk

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Scott", location_name = "Consultation Desk")
})
```

### Drop-in Desk

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Scott", location_name = "Drop-in Desk")
})
```

### Office

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Scott", location_name = "Office")
})
```


Scott Information
=====================================


Row {.tabset}
-------------------------------------

### Information Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Scott Information", location_name = "Information Desk")
})
```

### Information Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Scott Information", location_name = "Information Desk")
})
```


SMIL
=====================================


Row {.tabset}
-------------------------------------

### All (annual)


```{r}
renderPlot({
    construct_annual_chart(library_name = "SMIL")
})
 ```

### All (monthly)


```{r}
renderPlot({
    construct_monthly_chart(library_name = "SMIL")
})
 ```

### Circulation Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "SMIL", location_name = "Circulation Desk")
})
```

### Circulation Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "SMIL", location_name = "Circulation Desk")
})
```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "SMIL", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "SMIL", location_name = "Office")
})
```


Steacie
=====================================


Row {.tabset}
-------------------------------------

### All (annual)


```{r}
renderPlot({
    construct_annual_chart(library_name = "Steacie")
})
 ```

### All (monthly)


```{r}
renderPlot({
    construct_monthly_chart(library_name = "Steacie")
})
 ```

### Circulation Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Steacie", location_name = "Circulation Desk")
})
```

### Circulation Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Steacie", location_name = "Circulation Desk")
})
```

### Office (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Steacie", location_name = "Office")
})
```

### Office (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Steacie", location_name = "Office")
})
```

### Reference Desk (annual)

```{r}
renderPlot({
    construct_annual_chart(library_name = "Steacie", location_name = "Reference Desk")
})
```

### Reference Desk (monthly)

```{r}
renderPlot({
    construct_monthly_chart(library_name = "Steacie", location_name = "Reference Desk")
})
```
