---
title: "YUL Dashboard"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, echo=FALSE}
library(DT)
library(tidyverse)
library(flexdashboard)
library(lubridate)

## dashboard_data_dir <- paste0(Sys.getenv("DASHYUL_DATA"), "/viz/dashboard/")
dashboard_data_dir <- "/dashyul/data/viz/dashboard/"

## LibStats today

libstats_today <- read_csv(paste0(dashboard_data_dir, "libstats-today.csv"))

question.types <- c("1. Non-Resource", "2. Skill-Based: Tech Support", "3. Skill-Based: Non-Technical", "4. Strategy-Based", "5. Specialized")
nonresearch.questions <- question.types[1:3]
research.questions <- question.types[4:5]

desk_questions <- libstats_today %>% filter(location.name %in% c("Reference Desk", "Drop-in Desk"))
research_at_desk_count <- nrow(desk_questions %>% filter(question.type %in% research.questions))

office_questions <- libstats_today %>% filter(location.name == "Office")
research_in_office_count <- nrow(office_questions %>% filter(question.type %in% research.questions))

question_count_today_box <- function(library_name) {
  renderValueBox ({valueBox(libstats_today %>% filter(library.name == library_name) %>% summarise(count = n()) %>% select(count), icon = "fa-question") })
}

## LibStats summary

libstats_summary = read_csv(paste0(dashboard_data_dir,  "dashboard-libstats-daily-summary.csv"))

question_count_summary_box <- function(library_name) {
  renderValueBox ({valueBox(libstats_summary %>% filter(library.name == library_name) %>% summarise(total = sum(count)) %>% select(total), icon = "fa-question") })
}

libstats_summary_all_qs <- sum(libstats_summary$count)
libstats_summary_nonres_qs <- (libstats_summary %>% filter(question.type %in% nonresearch.questions))$count %>% sum
libstats_summary_res_qs <- libstats_summary_all_qs - libstats_summary_nonres_qs

## EZProxy
ezp_users_today     <- scan(paste0(dashboard_data_dir, "ezp-users-today.txt"))
ezp_users_yesterday <- scan(paste0(dashboard_data_dir, "ezp-users-yesterday.txt"))
new_ezp_users <- ezp_users_today - ezp_users_yesterday

ezp_daily_users <- read_csv(paste0(dashboard_data_dir, "dashboard-ezp-daily-users.csv"))
ezp_daily_users <- ezp_daily_users %>% filter(date <= Sys.Date() - days(2)) ## Drop the partial yesterday

platform_metrics <- read_csv("data/dashboard-platform-metrics.csv")

## Symphony

symphony_most_borrowed_titles <- read_csv(paste0(dashboard_data_dir, "symphony-most-borrowed-titles.csv"))
symphony_most_holded_titles   <- read_csv(paste0(dashboard_data_dir, "symphony-most-holded-titles.csv"))
symphony_borrows_per_day      <- read_csv(paste0(dashboard_data_dir, "symphony-borrows-per-day.csv"))

symphony_users_so_far <- scan(paste0(dashboard_data_dir, "symphony-users-so-far.txt"))
symphony_items_so_far <- scan(paste0(dashboard_data_dir, "symphony-items-so-far.txt"))

####
#### Digital repositories and platforms
####

## None of these are generating valid numbers, so don't use them (for now).

## ## YorkSpace
## yorkspace_numbers <- read_csv(paste0(dashboard_data_dir, "yorkspace-numbers.csv"))

## ## YUDL
## yudl_objects <- scan(paste0(dashboard_data_dir, "yudl-current-total-objects.txt"))

## ## OJS
## ojs_total_downloads <- scan(paste0(dashboard_data_dir, "ojs-total-downloads.txt"))


```


Row
-------------------------------------

### AskUs questions today

```{r}
question_count_today_box("AskUs")
```

### Building Services

```{r}
question_count_today_box("BuildingServices")
```

### ASC

```{r}
question_count_today_box("ASC")
```

### Bronfman

```{r}
question_count_today_box("Bronfman")
```

### Frost

```{r}
question_count_today_box("Frost")
```

### Maps

```{r}
question_count_today_box("Maps")
```

### Osgoode

```{r}
question_count_today_box("Osgoode")
```

### Scott

```{r}
question_count_today_box("Scott")
```

### SMIL

```{r}
question_count_today_box("SMIL")
```

### Steacie

```{r}
question_count_today_box("Steacie")
```


Row
-------------------------------------

### research qs at ref desks today

```{r}
gauge(research_at_desk_count, min = 0, max = nrow(desk_questions))
```

### research qs in offices today

```{r}
gauge(research_in_office_count, min = 0, max = nrow(office_questions))
```

Row
-------------------------------------

### questions asked since Sep 1

```{r}
renderValueBox ({valueBox(libstats_summary %>% summarise(total = sum(count)) %>% select(total), icon = "fa-question") })
```

### nonresearch questions

```{r}
gauge(libstats_summary_nonres_qs, min = 0, max = libstats_summary_all_qs)
```

### research questions

```{r}
gauge(libstats_summary_res_qs, min = 0, max = libstats_summary_all_qs)
```

Row
-------------------------------------

### people have used EZProxy since Sep 1

```{r}
renderValueBox({
    valueBox(ezp_users_today, icon = "fa-database")
})
```

### people used EZProxy yesterday for the first time this year

```{r}
renderValueBox({
    valueBox(new_ezp_users, icon = "fa-database")
})
```

### people have borrowed something since Sep 1

```{r}
renderValueBox({
    valueBox(symphony_users_so_far, icon = "glyphicon glyphicon-book")
 })
 ```

### items borrowed so far

```{r}
renderValueBox({
    valueBox(symphony_items_so_far, icon = "glyphicon glyphicon-book")
 })
 ```

<!-- ### checkouts of those items

```{r}
renderValueBox({
    valueBox(c(27342), icon = "glyphicon glyphicon-book")
 })
```
-->

<!-- Row
-------------------------------------

### YorkSpace items added since Sep 1 2016

```{r}
renderValueBox({
    valueBox(yorkspace_numbers$items_added, icon = "fa-database")
})
```

### YorkSpace downloads since Sep 1 2016

```{r}
renderValueBox({
    valueBox(yorkspace_numbers$author_downloads, icon = "fa-database")
})
```

### OJS downloads since Sep 1 2016

```{r}
renderValueBox({
    valueBox(ojs_total_downloads, icon = "fa-database")
})
```

### YUDL objects

```{r}
renderValueBox({
    valueBox(yudl_objects, icon = "fa-database")
})
```
-->

Row
-------------------------------------

### EZProxy platform metrics since Sep 1

```{r}
DT::renderDataTable(platform_metrics %>% arrange(desc(users)), rownames = FALSE)
```

### EZProxy users per day

```{r}
ggplot(ezp_daily_users, aes(x = date, y = users)) + geom_bar(stat = "identity") + labs(title = "EZProxy users per day", x = "", y = "")
```

Row
-------------------------------------

### most borrowed since Sep 1 2017

```{r}
DT::renderDataTable(symphony_most_borrowed_titles %>% arrange(desc(borrows)), escape = FALSE, rownames = FALSE)
## , include.rownames = FALSE, sanitize.text.function = function(x) x)
```

### items borrowed per day (not including accessories)

```{r}
ggplot(symphony_borrows_per_day, aes(x = date, y = borrows)) + geom_bar(stat = "identity") + labs(title = "Items borrowed per day", x = "", y = "")
```

Sidebar {.sidebar}
-------------------------------------

#### Étude

* [Étude](/etude/): student-centred view of collection use

#### Collections

* [ezproxy.interactive](/ezproxy.interactive/): details on EZProxy eresource use
* [CircYUL](/circyul/): circ histories (A2006–A2016)
* [YuColl](/yucoll/): growth and usage of the collection (A2005–A2016)
* [YuRang](/yurang/): compare p and e editions

#### Moodle

* [moodleviz](/moodleviz/): Library Resources Box impressions and clickthroughs

#### Desks

* [YuDesk2](/yudesk2/): desk analytics

#### Elsewhere

* [Google Analytics at York](http://analytics.info.yorku.ca/)
* [LibGuides usage statistics](http://researchguides.library.yorku.ca/admin_stats.php)
